We must Build these:

\begin{itemize}
\tightlist
\item
  free medicine
\item
  free transportation
\item
  free food
\item
  free water
\item
  free communication
\item
  free robots
\item
  free energy
\item
  free clothes
\item
  free art
\item
  free sex
\item
  free love
\item
  free books
\item
  free sports
\item
  free games
\end{itemize}

\textbf{Free Medicine.} This is perhaps the most transformative on the
list, and the most important. It is also a huge challenge and
potentially dangerous. Perhaps a good place to start is with medical
metrology. There needs to be technology which is free in the ways
described in this work which can be used to measure the purity of drugs.
Many illegal drugs are as dangerous as they are largely because they are
mixed heavily with mysterious random chemicals added by the capitalists
to increase their profits which are often poisons. We need to build up
the ability to measure the chemical content of street drugs fast and
accurately and with verification anyone can understand.

The other main points of early research effort should focus on either
the most ubiquitous or the most expensive life saving medications. We
must learn to use the techniques of brewing and genetically modified
microorganisms to make designer medicines, We need to build up the post
capitalist drug industry in a safe way by building the metrology into
every step to insure purity and safety.

The very early phases of Trash Magic need to focus on building
techniques and tools that are maximally general which can be used for
all drug development and production. The only way to do this efficiently
given how many life saving drugs we now depend on is to recruit heavily
from inside the existing biotechnology establishment. We need to find
the disgruntled geniuses in that system who are sick of it and desperate
for a way out. They often signed up for that industry to save lives and
find out they're part of a giant scam to rip off or kill the poor and
bleed everyone else and it's depressing and leads to a desire to leave
as well as to change our broken society. I do not anticipate that it
will be hard to find talented biotech experts who want to join us once
we've shown that our movement can do good science.

In keeping with the philosophy of Trash Magic, we want to integrate the
more traditional ``magical'' views of medicine with the
\emph{techniques} of modern medicine. That is, as with chemistry and
physics, the goal is to take the very valuable information contained in
modern science and reorganize that information in more human ways
looking to other models that exist in our history(various healing
traditions outside conventional Western medicine).

Finally I want to bring up another important technology to develop fast
in this process: imaging. We need FREE medical imaging. I have thoughts
on this, which will go in the second volume and probably the third
volume of this work, but I put this here as an open problem for the
reader in this volume.

\textbf{Free Transportation and shipping.} The ability to move freely
from one place to another is yet another basic human right which should
be guaranteed by a civilized society but which is denied in our current
system. What does free transportation look like? I think the lazy river
is a great example of a potentially free transport system. A lazy river
is a popular attraction at water parks in which an artificial river is
created which flows in a loop, allowing humans resting on inflatable
tubes to drift around the full loop over and over, getting in or out
anywhere.

I would propose that one of the most human friendly ways we could move
around is with a larger and more robust system of lazy rivers. We could
make waterways which are pumped using water power from the overall net
current. Ideally the water could be floated on with a variety of
inflatable personal watercraft which float around with no owner, waiting
to be used. This could involve staying dry or being partially immersed
or totally immersed, and it should include craft which can carry
substantial freight, also an essential use of transportation.

Obviously a giant lazy river with free boats is a massive challenge for
the early stages of this movement. I propose that a way to build useful
infrastructure now is to focus on rivers, and building transport for
goods that goes both ways with cables under the sea that can haul
freight upstream driven by the downstream flow. This could run
indefinitely with simple repairs over time, and could immediately be
used by many people for both utilitarian and artistic purposes. One
could put free stuff in the feed, let it flow up and down the stream,
and it could be grabbed and used by someone anywhere along the line.
This would mimic the basic functionality of the rotating sushi conveyor
belt, where a stationary person can see all possible types of sushi pass
by and grab what they want.

Another type of transportation which I think should exist after
capitalism is skylines. This is difficult, but worth building. As with
the lazy river, they will always go in loops, allowing people to get on
and off anywhere for free, ideally in either direction, but with ropes
or cables going infinitely, powered by ambient energy such as flowing
water or wind. These should have built in measurement technology that
allow users to see various safety parameters in real time and fix the
system as time passes. Skylines can also be suspended from various types
of aerostat, both hydrogen and soaring types.

I also imagine very slow moving giant spider robots which freely roam
the countryside, and which anyone can get on or off of at any time.
These might be many meters high, and have a whole industrial ecosystem
on board, including growing food, and a local culture which is spread as
the great lumbering spiderbot roams the world.

Finally, I must address the underlying issue of transportation in
capitalist society: much of it is to do things we don't really want to
do, and we won't have to do it anymore once capitalism falls apart. We
often travel to get things which should in be available locally but
which capitalism make only available in certain central locations, and
we \emph{mostly} travel to do work we don't want to do which no one
really needs done. We must end central industrial control of goods and
food and we must end the wage system. With these changes, and with a
free type of medicine anyone can get anywhere, we would only travel to
see friends and family and to have adventures. This changes the goals
enough that it will inevitably lead to drastic and unanticipated changes
in the structure of transportation in a post capitalist society.

\textbf{Free Food.} This is almost too obvious to go into much, as it's
where most anti-capitalists start. Food needs to be \emph{really} free,
though, using the stricter definitions of free from the second chapter
of this volume, rather than just ``no money'' type of free. This means
not only should you not have to spend work or time or money or minerals
to get food, food should simply exist in your world, around, moving on
its own using the types of transport systems described above. If you
want a carrot, just keep an eye out and a carrot will drift by on a
skyline or a hydraulic channel or a spiderbot. Since the technology of
automated food is so extensively studied in other people's work I will
be brief on this topic here.

\textbf{Free Water.} Water should be free! Truly free! Why is this so
hard for capitalists and their collaborators to understand? From our
standpoint, this means dirty water that will kill you should be turned
into clean water you can drink on its own, without any work, all the
time, with such plentitude that it is essentially a part of the natural
process of the world we live in. Capitalists already sort of do this
with their system of reservoirs that collect rain water, which is
essentially solar-purified water. They then hoard this and charge money
for it and centrally control it, of course.

Constructing infrastructure which directly converts smaller amounts of
water forever in different ways is key for freeing ourselves from the
Machine. This should exist, floating freely, in the ocean. Humanity must
return to the oceans, and we should bring fresh water with us. Huge
floating fresh water habitats should appear in the oceans.

Also, water purification should never be about just water. It should be
about the things we can remove from the water: heavy metals, salts,
biological chemicals, microorganisms, etc. All these should be
constantly observed by people, who can then use them as needed.

\textbf{Free Communication.} This is another place where I have to
distinguish between this project and the ``maker'' or ``hacker''
movements. To a typical mainstream hacker, a ``free'' phone would be one
with enough encryption to ensure total freedom from government
interference. This is not a useful definition of free. The world they
are building is one in which you replace the government snoops with
corporate technocrats who build your ``free'' gadgets. Nothing built by
a corporate technocrat is ever free. I would argue that free
communication means you don't have to have any interaction with the
technocratic priesthood at all. That means it is so simple to build,
edit, artistically enhance, and use that it's \emph{obvious}, and can be
done by anyone anywhere any time.

What does this mean in terms of practical technology? For one thing, way
more use of analog. One of the ways the technocratic priesthood has
built a strangle hold on our communications is by having so many layers
of horribly complicated digital software infrastructure that is needed
to do anything. End that.

I would say the starting point for our free communications network is
free space optical point to point analog voice links. This can be done
with the magic sticks in the earliest phase of this project, leading to
immediate deployment. Could encryption be used in this system? Sure,
yes. But do you really need encryption if you're using a system like
this? You're basically shining a flickering flashlight at someone. Going
optical(without lasers) is also important because it avoids conflict
with the government bodies that tightly control the frequencies normally
used for communication.

To be specific about what this will look like, it's the Trash Magic
Stick with all the aspects that go along with that. That means you get
it free as a gift normally, can easily build more and gift them on, and
it needs no grid energy to function, anyone can use it, etc. Using
vibrations of air and water to modulate fire, analog voice signals
should be made with light, and then photo diodes and amplifiers
demodulate the signal from a telescope built into the stick and play the
amplified sound directly out a speaker.

Free space point to point optical can be(and is being by capitalists)
scaled up to the global level. The capitalists have built so much dark
fiber in their speculative bubbles that we should be able to augment the
free space optical with free optical links in tunnels after things start
to fall apart on that side. Also while the capitalist Internet still IS
running, it should be possible to extend their networks all over using
optical repeater stations we can put in free in our between-the-cracks
infrastructure.

\textbf{Free Robots.}This topic is so important obviously it got its own
chapter but I'll briefly add here the reminder that a robot is not
really free unless you can build it yourself modified for \emph{your}
needs. That is, you can see a need, then build and program and use a
robot to fill that need, for pretty much any arbitrary need within the
scope of what a kind of robot can do. That is what makes it free. It is
very easy to fall into the trap of building robots that appear free but
still need a technocratic priesthood to function. Avoiding that is
probably the largest challenge of making truly free robots, as good
people have already been working on the other parts.

\textbf{Free Energy.}
