\section{Ent Moot}\label{ent-moot}

an ent is a slow moving giant tree robot that can walk, it can take
years for them to gather but they do gather, and along with their human
care takers build stuff together then move on, very slow

\section{Storm's a' commin'}\label{storms-a-commin}

A storm is coming! So many joules of energy! We will build all the
things, set things on fire, move heavy things around, describe the world
of the sunken city built back up from the water out of trash wizard
compontents

\section{wizards rolling in the
valley}\label{wizards-rolling-in-the-valley}

rolling robots going up and down the water, littoral robot ideas, using
the creek for power and trash sources, clean up the river, make habitats
etc.

\section{Ramblin' youth}\label{ramblin-youth}

young trash wizards gather for a giant party in the jungle, build crazy
shit

\section{Riding Against Thor: the story of warriors of the storm
stealing clean water from the gods of
Thunder}\label{riding-against-thor-the-story-of-warriors-of-the-storm-stealing-clean-water-from-the-gods-of-thunder}

LIke the other storm story but more epic and a smaller group of more
risk tolerant people, the warriors of the future, riding to glory by
harnessing the storm

Living in the deep ocean, on the surface, in the storms, giant systems
of mechanical oscillators that absorb the incoming energy of the storms
and turns it into useful work, processing sea water and trash at the
same time, storing energy, moving around, and making head, having a
fucking party.

Lazy river should be the main form of transportation in the future.
Humans should live in the river deltas of the world, in clean water
channels, in a civilization based on trash magic industry.

Bathtubs, where we are all The Dude in his bath with his joint and his
whale song music. THAT is the FUTURE.

The inundated cities of the future can be a paradise, with storms making
an ultimate comfort environment, light, sound, heat, air conditioning,
breezes, smells, vibrations, motions, lazy rivers, free drugs, all made
as the storms churn through, free energy free trash magic tools, free
food, free space and time.

Must build electric kayak ASAP.

Really huge diamondoid matrix going for a mile on each side around the
eye of a pacific storm, all made from trash, giant artificial mushrooms
float around inside the matrix, hookah smoking caterpillars.
